---
output: github_document
<<<<<<< HEAD
=======
always_allow_html: true
>>>>>>> cdc69c09892041ba776609bb52d0c72c0beb2a26
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
<<<<<<< HEAD
=======
require(mastercap)
load("data/raw_data.rda")

require(tidyverse)
>>>>>>> cdc69c09892041ba776609bb52d0c72c0beb2a26
```

# Mastercap Earthquake Data Visualization Package

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jgbond/mastercap.svg?branch=master)](https://travis-ci.com/jgbond/mastercap)
<!-- badges: end -->

The goal of this package ('mastercap') is to provide a few simple tools to make it easier to visualize earthquake data. It is part of the final capstone of the Mastering Software Development in R Coursera specialization.

The four main functions are:
1. clean_eq_data() takes raw earthquake data and reformats it into a tidy Tibble
2. geom_timeline() takes an earthquake Tibble and produces a visual timeline of earthquakes
3. geom_timeline_label() is the same as geom_timeline() but also adds labels
4. eq_map() plots earthquakes on an interactive, annotated map

## Example

The first example cleans the raw data and produces an earthquake timeline to display earthquakes in China, Russia, and Japan between Jan 1, 2008, and Jan 1, 2010.

<<<<<<< HEAD
```{r}
library(mastercap)
data("raw_data.rda")
=======
```{r echo = TRUE}
>>>>>>> cdc69c09892041ba776609bb52d0c72c0beb2a26
raw_data %>%
  clean_eq_data() %>%
  geom_timeline(mindate = "2008-01-01",
                maxdate = "2010-01-01",
                countries = c("China", "Russia", "Japan"))
```

The second example demonstrates the same plot but uses the geom_timeline_label function.

<<<<<<< HEAD
```{r}
library(mastercap)
data("raw_data.rda")
=======
```{r echo = TRUE}
>>>>>>> cdc69c09892041ba776609bb52d0c72c0beb2a26
raw_data %>%
  clean_eq_data() %>%
  geom_timeline_label(mindate = "2008-01-01",
                      maxdate = "2010-01-01",
                      countries = c("China", "Russia", "Japan"))
```

The final example demonstrates eq_map. It uses the same filtered data.

<<<<<<< HEAD
```{r}
library(mastercap)
data("raw_data.rda")
raw_data %>%
  clean_eq_data() %>%
  filter(date >= "2008-01-01",
=======
```{r echo = TRUE}
raw_data %>%
  clean_eq_data() %>%
  dplyr::filter(date >= "2008-01-01",
>>>>>>> cdc69c09892041ba776609bb52d0c72c0beb2a26
         date <= "2010-01-01",
         country == c("China", "Russia", "Japan")) %>%
  eq_map()
```

